Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-31 analysis/paper/paper.qmd
Fixed missing name of zones for the eco-forest figure

SPACIAL ANAlysis
@prates2022changes

>>>>

SPACIAL ANAlysis @prates2022changes provde strong relationship between the temporal density and spatial distribution of megafauna and Fishtail projectile points, and proposed that this weapon was designed and used for megafauna hunting, contributing to their extinction by exploring changes in projectile point technology, as well as the body mass of potential megafaunal prey, and show that Fishtails were strongly related to the largest extinct megafaunal species.
